Changes in accessibility to foodbanks during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario

### 2021-04-22 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.Rmd
Fixed error in loading data

```{r invoke-data, include=FALSE}
data(data_da_2016)
data(dwelling_network_points_2016)
#data(hamilton_boundary)
data(population_age_income)
data(foodbank_locations)
data(modes_less40k)
data(ttm_car)
data(ttm_transit)
data(ttm_walk.RData)
```

>>>>

```{r invoke-data, include=FALSE}
data(data_da_2016)
data(dwelling_network_points_2016)
#data(hamilton_boundary)
data(population_age_income)
data(foodbank_locations)
data(modes_less40k)
data(ttm_car)
data(ttm_transit)
data(ttm_walk)
```
